### 2022-07-22 paper/paper.tex
tilde x

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and ends with searching task completed. The URTS is composed of $N$ teams and a ground station. Each team contains $1$ UAV and $M-1$ robots. The $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,M$ and $j=1,2,...,N$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\section{Reference Tracking control}
00
After the reference trajectory is set, the last step is to design a controller for a agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor. Besides, its integration $\int_{0}^{t} x(\tau) d\tau$ and differentiation $\dot{x}(t)$ can also be measured by sensor respectively for PID control. Then, the output equation can be formulated as:
\begin{equation} \label{eq:agent output}
    y(t) = C\pmb{x}(t)
\end{equation}
where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is a known output matrix, and $\pmb{x}(t)=\begin{bmatrix}
    \int_{0}^{t} x^T(\tau) d\tau & x^T(t) & \dot{x}^T(t)
\end{bmatrix}^T$. Futhermore, to make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists
    \begin{enumerate*}
        \item coupling effect due to co-channel interference in communication between agents and
        \item cyber-attack on communication network between agents and ground station.
    \end{enumerate*}
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Suppose the above disturbances can be equivalently expressed as the disturbances $d_i(t), i=1,2$ in the nominal model (\ref{eq:agent}) and (\ref{eq:agent output}), the real agent model is given as:
\begin{equation} \label{eq:nonlinear sys} 
    \begin{split}
        & M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t) = u(t)\\
        & y(t) = C\pmb{x}(t) + d_2(t)
    \end{split}
\end{equation}
For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed. Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.

\subsection{$H_\infty$ observer-based PID FTC for linear system}
Given a linear system with fault signals:
\begin{equation} \label{eq:4}
    \begin{split}
        & \dot{x}(t)=Ax(t)+B(u(t)+f_1(t)) \\
        & y(t)=Cx(t)+f_2(t)   
    \end{split}  
\end{equation}
where $x(t)\in\mathbb{R}^n$, $u(t)\in\mathbb{R}^m$, $y(t)\in\mathbb{R}^l$, and $f_i:\mathbb{R}\rightarrow \mathbb{R}^{n_i}, f_i(t)\in C^{1}, i=1,2$ with $n_1=m$ and $n_2 = l$.

\textit{
    \begin{remark}
        The fault signal $f_i(t), i=1,2$ are assumed to be smooth rather than bounded, which will make the proposed method more general for practical scenario.
    \end{remark}
}

From finite difference method, the derivative of the fault signals $\dot{f}_i(t), i=1,2$ with uniform grid $h$ can be expressed as:
\begin{equation} \label{eq:df}
    \dot{f}_i(t)=\sum_{k\in{Z_0}}\frac{a_k f_i(t-kh)}{h} + R_{p-1}(t), Z_0\subset\mathbb{Z}
\end{equation}
where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference. For constructing a state-space representation, the derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed. For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$. Then, we can obtain the following equation by (\ref{eq:df}) by changing index $k$ to $j$:
\begin{equation} \label{eq:df1}
    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t), j=0,1,\dots,p-1
\end{equation}
where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
\begin{equation} \label{eq:7}
    \dot{F}_i(t)=A_iF_i(t)+v_i(t)
\end{equation}
where $v_i(t)=\begin{bmatrix}
    \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
\end{bmatrix}^T$, $F_i(t)=\begin{bmatrix}
    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n_i}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
\begin{equation} \label{eq:8}
    f_i(t)=C_iF_i(t)
\end{equation}
where $C_i=\begin{bmatrix}
    1 & 0 & \dots & 0
\end{bmatrix}\otimes I_{n_i}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:4}), we get:
\begin{equation} \label{eq:9}
    \begin{split}
        & \dot{\bar{x}} = \bar{A}\bar{x}+\bar{B}u+\bar{v} \\
        & y=\bar{C}\bar{x}
    \end{split}
\end{equation}
where $\bar{x} = \begin{bmatrix}
    x \\ F_1 \\ F_2
\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
    A & BC_1 & 0 \\
    0 & A_1 & 0 \\
    0 & 0 & A_2
\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
    B \\ 0 \\ 0
\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
    C & 0 & C_2
\end{bmatrix}$, and $\bar{v}=\begin{bmatrix}
    0 \\ v_1 \\ v_2
\end{bmatrix}$. Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimat them and origin state simutaniously:
\begin{equation} \label{eq:10}
    \begin{split}
        & \dot{\hat{\bar{x}}}=\bar{A}\hat{\bar{x}}+\bar{B}u+{L}(y-\hat{y}) \\
        & \hat{y}=\bar{C}\hat{\bar{x}}  
    \end{split}
\end{equation}
\begin{assumption}
    The augmented system (\ref{eq:9}) is observable.
\end{assumption}
The PID FTC law is given as:
\begin{equation} \label{eq:11}
    u=K\hat{\bar{x}}
\end{equation}
where $K = \begin{bmatrix}
    K_I & K_P & K_D & K_{F_1} & K_{F_2}
\end{bmatrix}$ is total control gain, $K_P,K_I,K_D$ are PID control gain, and $K_{F_i}, i=1,2$ are fault control gain. Let us define the estimation error $\hat{\bar{e}}=\bar{x}-\hat{\bar{x}}$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
\begin{equation} \label{eq:aug}
    \dot{\tilde{x}} = \tilde{A}\tilde{x}+\tilde{v}
\end{equation}
where $\tilde{x}=\begin{bmatrix}
    \bar{x} \\ \hat{\bar{e}}
\end{bmatrix}$, $\tilde{A}=\begin{bmatrix}
    \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
\end{bmatrix}$, and $\tilde{v}=\begin{bmatrix}
    \bar{v} \\ 0
\end{bmatrix}$

The tracking control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
\begin{equation} \label{Hinf}
    H_{\infty}(K, L) = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2 
\end{equation}
where $t_f$ is the final time, $Q > 0$ is the weighting matrix of tracking and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated. If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy. To find these gains, the following theroem is given.
\begin{theorem} \label{theorem1}
    If
    $$\begin{bmatrix}
        & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
        & \ast  & M_{22} & 0 & P_2 \\
        & \ast & \ast & -I & 0 \\
        & \ast & \ast & \ast & -\rho^2 
    \end{bmatrix}\leq 0 $$
    where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$. Then system (\ref{eq:aug}) achieve $H_\infty$ observer-base stabilized control performance (\ref{Hinf}).
\end{theorem}
\begin{proof}
    proof...
\end{proof}

\subsection{$H_\infty$ observer-based feedback linearization-based PID FTC for agents}
If we can transform the nonlinear system (\ref{eq:nonlinear sys}) to a linear system, the tracking problems for UAV and robot can be solved by Theorem \ref{theorem1}. An feedback linearization-based control law is uesd to solve this issue, which is given as follow:
% To obtain state variable by output measurement, an observer is proposed:
% \begin{equation} \label{eq:nonlinear obs} 

@@

%         & u(t) = M(\hat{x}(t))\ddot{\hat{x}(t)} + H(\hat{x}(t),\dot{\hat{x}(t)})\\
%         & \hat{y}(t) = C\hat{x}(t)

@@

    u(t)= M(x_e(t))(\ddot{r}(t) + u_{fb}(t)) + H(x_e(t),\dot{x}_e(t))    
    % & u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F} \\ 
where $x_e(t)=x(t) + \Delta e(t)$, $\Delta e(t)=e(t)-\hat{e}(t)$ is the error between tracking error $e(t) = x(t) - r(t)\in\mathbb{R}^n$ and estimation of tracking error $\hat{e}(t)$, $u_{fb}(t)$ is feedback control law, and the other term in (\ref{eq:control}) is feed-foward control law for canceling nonlinearity. Substitute (\ref{eq:control}) into state equation (\ref{eq:nonlinear sys}), we get:
\begin{equation}\begin{split} \label{eq:21}
    & M(x_e(t))(\ddot{r}(t) + u_{fb}) + H(x_e(t),\dot{x}_e(t)) \\
    & = M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t)       

@@

By subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides of (\ref{eq:21}):
\begin{equation} \label{eq:22}
    -\Delta M \ddot{r}(t) + M(x_e(t))u_{fb} = M(x(t))\ddot{e}(t) + \Delta H + d_1(t)

@@

where $\Delta M = M(x(t)) - M(x_e(t)), \Delta H = H(x(t),\dot{x}(t)) - H(x_e(t),\dot{x}_e(t))$ is the error terms due to difference between true state and estimated state. By Multipling $M(x(t))^{-1}$ from the left and right sides of (\ref{eq:22}) with arrangment, we have:
    \ddot{e}(t) = u_{fb}(t) + d_3(t)
where $d_3(t) = -M(x(t))^{-1}(\Delta M(\ddot{r}(t)+u_{fb}) + \Delta H + d_1(t))$. Let $\pmb{e}(t)=\begin{bmatrix}

@@

\begin{equation} \label{eq:24}
    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t))

@@

\end{bmatrix} $. Since $C$ is known, we can let $\pmb{y}(t) = y(t) - C\pmb{r}(t)\in\mathbb{R}^{ln}$ where $\pmb{r}(t) = \begin{bmatrix}
    \int_{0}^{t} r^T(\tau) d\tau & r^T(t) & \dot{r}^T(t)
\end{bmatrix}^T$. Then, the output equation in (\ref{eq:nonlinear sys}) can be modified as:
\begin{equation} \label{eq:25}
    \pmb{y}(t) = C\pmb{e}(t) + d_2(t)
% where $d_4(t) = \Delta C + d_3(t)$ with $\Delta C = C(x(t)-\hat{x}(t))$. 
Combining (\ref{eq:24}) and (\ref{eq:25}), we obtain the linearized system:
\begin{equation} \label{eq:linear sys}
        & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t)) \\
        & \pmb{y}(t)=C\pmb{e}(t)+d_2(t)   
By Theorem \ref{theorem1}, the form show that the system (\ref{eq:nonlinear sys}) can achieve $H_\infty$ performance with the observer
\begin{equation} \label{eq:linear obs}
        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t) + \bar{B}u_{fb}(t) + L(\pmb{y}(t)-\hat{y}(t)) \\
        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)   
and the control law (\ref{eq:control})
where $\hat{\bar{e}}(t)=\begin{bmatrix}
    \hat{\pmb{e}} \\ \hat{F}_1 \\ \hat{F}_2
\end{bmatrix}$, $\hat{\pmb{e}} = \begin{bmatrix}
    \int_{0}^{t} \hat{e}(\tau) d\tau \\ \hat{e}(t) \\ \dot{\hat{e}}(t)
\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
    A & BC_1 & 0 \\
    0 & A_1 & 0 \\
    0 & 0 & A_2
\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
    B \\ 0 \\ 0
\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
    C & 0 & C_2
\end{bmatrix}$, and $u_{fb}=K\hat{\bar{e}}$.
\textit{
    \begin{remark}
        Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
    \end{remark}
}

>>>>

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and ends with searching task completed. The URTS is composed of $N_j$ teams and a ground station. Each team contains $1$ UAV and $N_i-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_i$ and $j=1,2,...,N_j$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. The control law is given as:
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms to canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law. To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9448458}.
    \item For agent, there exists cyber-attack on communication network between agents and ground station.
    \item For agent, there exists sensor noise.
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to an disturbance force $d_1(t)$. The nominal system (\ref{eq:agent}) then be rewrited as the real system:
% The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
\begin{equation} \label{eq:agent d1} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + d_1(t)
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}

@@

%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F

@@

% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(r(t))\ddot{x}(t)$ from the left and right sides, we have:
\begin{equation} \label{eq:agent1}
        & (M(x(t))-M(r(t)))\ddot{x}(t) + H(x(t),\dot{x}(t)) \\
        & =(M(r(t))(\ddot{r}(t)-\ddot{x}(t)) + M(r(t))u_{fb}(t) \\
        & + H(r(t),\dot{r}(t)) + d_1(t)

@@

By Multipling $M(r(t))^{-1}$ from the left and right sides and with some arrangments, we have:
    \ddot{e}(t) = u_{fb}(t) + f_1(t)

@@

where $f_1(t) = M(r(t))^{-1}(-\Delta M(\ddot{x}(t)) -\Delta H + d_1(t))$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensationand, and $e(t)= x(t)-r(t)$ is the tracking error.
% \textit{
%     \begin{remark}
%         Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
%     \end{remark}
% }
Let $\pmb{e}(t)=\begin{bmatrix}

@@

\begin{equation} \label{eq:linear f1}
    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t))

@@

\end{bmatrix}$.

Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the fault tolerance stable control problem of linear system (\ref{eq:linear f1}). The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make it stable. In a real system, the feedback information is measured by sensor, i.e, the state $\pmb{e}(t)$ in (\ref{eq:linear f1}) is unavailable. As mentioned before, the external disturbances on sensor also need to be considered. Since the sensor information (\ref{eq:agent output}) will transmitted back to the ground station through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are considered. The total effect can be equivalent to an sensor fault signal $f_2(t)$. The measurement output equation is formulated as:
\begin{equation} \label{eq:agent output}
    y(t) = C\pmb{e}(t) + f_2(t)
\end{equation}
where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is output matrix. By combining (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have:
\begin{equation} \label{eq:4}
    \begin{split}
        & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t)) \\
        & y(t) = C\pmb{e}(t) + f_2(t)   
    \end{split}  
\end{equation}
where $x(t)\in\mathbb{R}^n$, $u(t)\in\mathbb{R}^m$, $y(t)\in\mathbb{R}^l$, and $f_i:\mathbb{R}\rightarrow \mathbb{R}^{n_i}, f_i(t)\in C^{1}, i=1,2$ with $n_1=m$ and $n_2 = l$.
% For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed. Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.
\textit{
    \begin{remark}
        The fault signal $f_i(t), i=1,2$ are assumed to be smooth rather than bounded, which will make the proposed method more general for practical scenario.
    \end{remark}
}

From finite difference method, the derivative of the fault signals $\dot{f}_i(t), i=1,2$ with uniform grid $h$ can be expressed as:
\begin{equation} \label{eq:df}
    \dot{f}_i(t)=\sum_{k\in{Z_0}}\frac{a_k f_i(t-kh)}{h} + R_{p-1}(t), Z_0\subset\mathbb{Z}
\end{equation}
where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference. For constructing a state-space representation, the derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed. For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$. Then, we can obtain the following equation by (\ref{eq:df}) by changing index $k$ to $j$:
\begin{equation} \label{eq:df1}
    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t), j=0,1,\dots,p-1
\end{equation}
where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
\begin{equation} \label{eq:7}
    \dot{F}_i(t)=A_iF_i(t)+v_i(t)
\end{equation}
where $v_i(t)=\begin{bmatrix}
    \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
\end{bmatrix}^T$, $F_i(t)=\begin{bmatrix}
    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n_i}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
\begin{equation} \label{eq:8}
    f_i(t)=C_iF_i(t)
\end{equation}
where $C_i=\begin{bmatrix}
    1 & 0 & \dots & 0
\end{bmatrix}\otimes I_{n_i}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:4}), we get:
\begin{equation} \label{eq:9}
    \begin{split}
        & \dot{\bar{e}}(t) = \bar{A}\bar{e}(t)+\bar{B}u_{fb}(t)+\bar{v}(t) \\
        & y(t)=\bar{C}\bar{e}(t)
    \end{split}
\end{equation}
where $\bar{e}(t) = \begin{bmatrix}
    \pmb{e}(t) \\ F_1 \\ F_2
\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
    A & BC_1 & 0 \\
    0 & A_1 & 0 \\
    0 & 0 & A_2
\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
    B \\ 0 \\ 0
\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
    C & 0 & C_2
\end{bmatrix}$, and $\bar{v}(t)=\begin{bmatrix}
    0 \\ v_1(t) \\ v_2(t)
\end{bmatrix}$. Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimat them and origin state simutaniously:
\begin{equation} \label{eq:10}
    \begin{split}
        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{x}}(t)+\bar{B}u_{fb}(t)+{L}(y(t)-\hat{y}(t)) \\
        & \hat{y}(t)=\bar{C}\hat{\bar{x}}(t)  
    \end{split}
\end{equation}
\begin{assumption}
    The augmented system (\ref{eq:9}) is observable.
\end{assumption}
The PID FTC law is given as:
\begin{equation} \label{eq:11}
    u_{fd}(t)=K\hat{\bar{e}}(t)
\end{equation}
where $K = \begin{bmatrix}
    K_I & K_P & K_D & K_{F_1} & K_{F_2}
\end{bmatrix}$ is total control gain, $K_P,K_I,K_D$ are PID control gain, and $K_{F_i}, i=1,2$ are fault control gain. Let us define the estimation error $\tilde{e}=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
\begin{equation} \label{eq:aug}
    \dot{\tilde{x}}(t) = \tilde{A}\tilde{x}(t)+\tilde{v}(t)
\end{equation}
where $\tilde{x}(t)=\begin{bmatrix}
    \bar{e}(t) \\ \tilde{e}(t)
\end{bmatrix}$, $\tilde{A}=\begin{bmatrix}
    \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
\end{bmatrix}$, and $\tilde{v}(t)=\begin{bmatrix}
    \bar{v}(t) \\ 0
\end{bmatrix}$

The tracking control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
\begin{equation} \label{Hinf}
    H_{\infty}(K, L) = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2 
\end{equation}
where $t_f$ is the final time, $Q > 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated. If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy. To find these gains, the following theroem is given.
\begin{theorem} \label{theorem1}
    If
    $$\begin{bmatrix}
        & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
        & \ast  & M_{22} & 0 & P_2 \\
        & \ast & \ast & -I & 0 \\
        & \ast & \ast & \ast & -\rho^2 
    \end{bmatrix}\leq 0 $$
    where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$. Then system (\ref{eq:aug}) achieve $H_\infty$ observer-base stabilized control performance (\ref{Hinf}).
\end{theorem}
\begin{proof}
    proof...
\end{proof}

% \begin{equation}      
%     u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F}
% \end{equation}
